\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}

### 2017-07-08 Manuscript.Rmd
Predicted biomass for each site

>>>>

```{r Predicted biomass for each site}
Predicted_biomass <- fish %>% 
  mutate(This = review$a[14] * (Length^review$b[14]), 
         APA = review$a[1] * (Length^review$b[1]),
         APF = review$a[2] * (Length^review$b[2]),
         APM = review$a[3] * (Length^review$b[3]),
         Sandel = review$a[4] * (Length^review$b[4]),
         Chin = review$a[5] * (Length^review$b[4]),
         Barbour = review$a[6] * (Length^review$b[6]),
         deLeon = review$a[7] * (Length^review$b[7]),
         FoggA = review$a[8] * (Length^review$b[8]),
         FoggM = review$a[9] * (Length^review$b[9]),
         FoggF = review$a[10] * (Length^review$b[10]),
         Edwards = review$a[11] * (Length^review$b[11]),
         Sabido = review$a[12] * (Length^review$b[12]),
         FishBase = review$a[13] * (Length^review$b[13])) %>% 
  group_by(Location) %>% 
  summarize(Observed = sum(Weight),
            This = sum(This)/Observed,
            APA = sum(APA)/Observed,
            APF = sum(APF)/Observed,
            APM = sum(APM)/Observed, 
            Sandel = sum(Sandel)/Observed,
            Chin = sum(Chin)/Observed,
            Barbour = sum(Barbour)/Observed,
            deLeon = sum(deLeon)/Observed,
            FoggA = sum(FoggA)/Observed,
            FoggM = sum(FoggM)/Observed,
            FoggF = sum(FoggF)/Observed,
            Edwards = sum(Edwards)/Observed,
            Sabido = sum(Sabido)/Observed,
            FishBase = sum(FishBase)/Observed) %>% 
  ungroup() %>% 
  gather(Study, Biomass, -Location)
```

```{r plot comparing predictions, include = F}
Predicted_biomass_plot <-   Predicted_biomass %>% 
  filter(!Study == "Observed") %>% 
  ggplot(aes(x = Study, y = Biomass)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0, size = 1) +
  stat_summary(geom = "point", fun.y = "mean", fill = "blue", size = 3, shape = 21) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  labs(y = "Biomass (Predicted / Observed)") +
  coord_flip() +
  theme_bw() +
  theme(text = element_text(family = "Times"))

Predicted_biomass_plot
```
